### 2017-01-18 robust-checks.tex
Minor tidying up and reformatting the checklist

\begin{easylist}[checklist]
& Use version control.

& Document your code and usage
&& Explain what the software does.
&& List required dependencies.
&& Provide compilation/installation instructions.
&& List input and output files.
&& State attributions and licensing.
&& Print usage information when launching from the command line.
&& Desribe the syntax for running the program.
&& Explain the software's primary function.
&& Describe the most commonly used arguments, with a description of each and default values.
&& Tell users where to find more information.
&& Print to standard output.
&& Exit with an appropriate exit code

@@

& Version your releases.
&& Increment your version number every time you release your software to other people.
&& Print the version number when given the appropriate flag.
&& Include the version number in all of the program's output.
&& Ensure that old released versions continue to be available.

& Reuse software (within reason).
&& Make sure that you really need auxiliary programs.
&& Ensure the appropriate software and version is available.
&& Ensure that reused software is robust.

@@

& Do not require root or other special privileges to install or run.
&& Packages should not require root privileges to set up or use.
&& Allow packages to be installed in an arbitrary location.
&& Ask another person to try and build your software before releasing it.

@@

& Produce identical results when given identical inputs.
&& Echo all parameters and software versions to standard out or a log file alongside the results.
&& A particular version of a program should produce the same results every time it is run.
&& Allow the user to optionally provide the random seed as an input parameter.
&& Make sure the acceptable tolerance is known and detailed in documentation and in the tests.

>>>>

\begin{easylist}[checklist]
& Use version control.
&& Put everything created manually into version control as soon as it is created.

& Document your code and usage.
&& Write a good README file.
&& Print usage information.

@@

& Version your releases.
&& Increment your version number every time you release your software to other people.
&& Make the version of your software easily available by supplying \texttt{-\/-version} or \texttt{-v} on the command line.
&& Include the version number in in all of the program's output.
&& Ensure that old released versions continue to be available.

& Reuse software (within reason).
&& Make sure that you really need the auxiliary program.
&& Ensure the appropriate software and version is available.
&& Ensure that reused software is robust.

@@

& Do not require root or other special privileges to install or run.
&& Do not require root privileges to set up or use packages.
&& Allow packages to be installed in an arbitrary location.
&& Ask another person to try and build your software before releasing it.

@@

& Produce identical results when given identical inputs.
&& Echo all parameters and software versions to standard out or a log file alongside the results.
&& Produce the same results each time the same version of the program is run with the same inputs.
&& Allow the user to optionally provide the random seed as an input parameter.
&& Make sure acceptable tolerances are known and detailed in documentation and tests.
